Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-08 appendix.tex
tex

@@

 [T] APGD as the optimization algorithm? | postpone.
	Just shifting robustness of all methods down by a bit.
	Robust methods are still robust. Unrobust methods are still not robust.
\end{comment}

>>>>

(6) \ul{Optimization algorithm for adversarial attacks.}

In this paper, PGD~\cite{madry} is adopted as the optimization algorithm for
creating adversarial examples.
%
It is also adopted by the ERS metric~\cite{robrank} for robustness evaluation
with a collection of white-box attacks.
%
In the literature, some other optimization methods exists, such as
APGD~\cite{apgd}.
%
However, we adopt PGD~\cite{madry} to keep aligned with the state-of-the-art
work for sake of fair comparison.

A replacement of such algorithm for adversarial training will affect the
model's performance on benign examples and robustness.
%
Stronger adversarial examples during adversarial training may further boost the
robustness of a model, and further reduce the performance on benign examples.

A replacement of such algorithm for ERS evaluation will affect the robustness
score for all existing methods.
%
All existing methods are expected to have a lower (to a certain extent)
robustness against a stronger algorithm than PGD.
%
In this case, a robust method still remains robust, and a not robust method
remains not robust.

@@

\end{comment}
